---
title: "README"
author: "Jonathan De Smedt"
date: "14-4-2020"
output: 
  md_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## RtqpcR: Analysis of RT-qPCR expression data.

This package facilitates the analysis of RT-qPCR expression data (reverse transcriptase quantitative polymerase chain reaction). Here below we provide a tutorial for a standard qPCR analysis.

## Dependencies

Before starting any qPCR analysis, please install the following packages:

```{r, eval=FALSE, results='asis', message=FALSE}
BiocManager::install("readxl")
BiocManager::install("dplyr")
BiocManager::install("ggplot2")
```

## Installation

Install the RTqpcR package by running:

```{r, eval=FALSE, results='asis', message=FALSE}
devtools::install_github("jonathandesmedt92/RtqpcR")
library(RtqpcR)
```


## Tutorial

# Reading the raw expression data.

To date, RtqpcR is only compatible with qPCR data from a Viaa7 platform (384-well plates). The first step is to read in the expression data. At this point, the user has to decide how to deal with undetected mRNA expression values. We generally recommend setting these expression values to 40 (i.e. maximal CT value). These values will be plotted in graphs, however they will not be included in statistical analyses.

```{r, eval=TRUE, message=FALSE}
# Initialise an RtqpcR object
obj<-qpcr()

# Read in the expression data
obj<-read_qpcr(qpcr = obj, files = "data/test.xlsx")

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
